Results MSRC latent class analysis

### 2021-06-07 manuscript/manuscript.Rmd
comment out n

```{r tabcat, include = TRUE}
ct_dct <- cat_dict
names(ct_dct) <- toupper(names(ct_dct))
#c("METHOD", "GENDER", "RACE", "ANY_SERVICE")
cats <- do.call(rbind, lapply(names(res_cat), function(thename){
  x <- res_cat[[thename]]
  out <- x$parameters[, c("class", "category", "prob", "se")]
  out$ci <- tidySEM::conf_int(as.numeric(out$prob), se = as.numeric(out$se))
  out <- reshape(out, v.names = c("prob", "se", "ci"), timevar = "class", idvar = "category", direction = "wide")
  out$chisq <- NA
  out$p <- NA
  out$cramersv <- NA
  out$chisq[1] <- x$tests$chi_square
  out$p[1] <- x$tests$p
  the_n <- x$tests$n
  if(is.null(the_n)) the_n <- res_cont$summaries$Observations
  out$cramersv[1] <- sqrt((as.numeric(x$tests$chi_square)/as.numeric(the_n))/1)
  out <- cbind(Variable = NA, out)
  out$Variable[1] <- thename
  out$category <- ct_dct[[thename]][out$category]
  out
}))
test_res <- sapply(res_catdum, function(x){x$tests$p[1]})
names_testres <- unique(gsub(".$", "", names(test_res)))
test_res <- lapply(names_testres, function(x){test_res[grep(x, names(test_res))]})
names(test_res) <- names_testres
#test_res <- test_res[na.omit(pmatch(na.omit(cats$Variable), names(test_res)))]

>>>>

```{r tabcat, include = TRUE}
ct_dct <- cat_dict
names(ct_dct) <- toupper(names(ct_dct))
#c("METHOD", "GENDER", "RACE", "ANY_SERVICE")
cats <- do.call(rbind, lapply(names(res_cat), function(thename){
  x <- res_cat[[thename]]
  out <- x$parameters[, c("class", "category", "prob", "se")]
  out$ci <- tidySEM::conf_int(as.numeric(out$prob), se = as.numeric(out$se))
  out <- reshape(out, v.names = c("prob", "se", "ci"), timevar = "class", idvar = "category", direction = "wide")
  out$chisq <- NA
  out$p <- NA
  out$cramersv <- NA
  #out$n <- NA
  out$chisq[1] <- x$tests$chi_square
  out$p[1] <- x$tests$p
  the_n <- x$tests$n
  if(is.null(the_n)) the_n <- res_cont$summaries$Observations
  out$cramersv[1] <- sqrt((as.numeric(x$tests$chi_square)/as.numeric(the_n))/1)
  out <- cbind(Variable = NA, out)
  out$Variable[1] <- thename
  out$category <- ct_dct[[thename]][out$category]
  out
}))
test_res <- sapply(res_catdum, function(x){x$tests$p[1]})
names_testres <- unique(gsub(".$", "", names(test_res)))
test_res <- lapply(names_testres, function(x){test_res[grep(x, names(test_res))]})
names(test_res) <- names_testres
#test_res <- test_res[na.omit(pmatch(na.omit(cats$Variable), names(test_res)))]
